### 2012-06-07 notes/coop.tex
Notes

@@

Consider first the case of a finite set or players $N$. Let \pi be a permutation of $N$.

@@

\hline

@@

\hline

\end{document}

>>>>

\usepackage{amsfonts}
\usepackage{amssymb}

@@

Consider first the case of a finite set or players $N$. Let $\pi$ be a permutation of $N$.

@@

\hrule

@@

\hrule

In this paper we denote by $\mathbb{R}$ the set of all real numbers. The $general coalition game$ (or beifly the game) is a pair ($I$, $V$),
where $I$ is a non-empty and finite set and $V$ is a mapping associating any subset $K$ of $I$ witha subset of the real space $\mathbb{R}^I$ and preserving the following properties for any $K \subset I$.
(1..4)
The elements of the set $I$ are called players, its subsets are $coalitions$ and its partitions into non-empty disjoint coalitions are called $coalition structures$. The real-valued vectors from $\mathbb{R}^I$ are called $imputations$ and the sets $V(K), K \subset I,$ represent the sets of all imputations achievable by the coalition $K$. The mapping $V$ of $2^I$ into the class of subsets of $\mathbb{R}^I$ is called $generalized characterestic function$. 
\end{document}
